### 2023-06-15 README.Rmd
230615_001

```{r}
createHOT(
  data = CBC,
  id = 1,
  None = 21,
  prod = 3,
  prod.levels = list(c(4, 9, 19), c(8, 12, 17), c(5, 10, 17)),
  coding = c(0, 0, 0),
  method = "CBC",
  choice = 22
)
```

@@

```{r}
CBC$Group <- base::factor(CBC$Group,
                          levels = c(1:3),
                          labels = paste0("Group_", c(1:3)))
```

>>>>

```{r}
HOT <- createHOT(
  data = CBC,
  id = 1,
  None = 21,
  prod = 3,
  prod.levels = list(c(4, 9, 19), c(8, 12, 17), c(5, 10, 17)),
  coding = c(0, 0, 0),
  method = "CBC",
  choice = 22
)
```

@@

```{r}
CBC$Group <- base::factor(CBC$Group,
  levels = c(1:3),
  labels = paste0("Group_", c(1:3))
)
```
